\bf Title here

### 2022-11-17 project/PaperTemplate/paper.Rmd
Almost done w percentile method

Exposition
-> what is a bootstrap
--> parametric
--> non-parametric
--> briefly: what is jackknife
--> SE and bias?
-> what is a bootstrapped confidence interval
--> what can it do
-> how do we create them
-> different types of bootstrapped CI
--> standard t interval, approx classical, swapped SE, percentile, Bias-corrected, BCa
---> for sample mean or corr (check example sheet)

Bootstrapping is a statistical method of resampling that allows the estimation of a test statistic from an unknown distribution. Supposing we have a random sample $X = (x_1,x_2,\dots,x_n)$, then the bootstrap sample could be represented as $X^* = (x^*_1, x^*_2, \dots, x^*_n)$ where each $x^*_i$ is sampled randomly with equal probability and with replacement from $\{x_1,x_2,\dots,x_n\}$. From this bootstrap sample, a bootstrap replication of the test statistic can be computed.

>>>>

Exposition
-> what is a bootstrap
--> parametric
--> non-parametric
--> briefly: what is jackknife nah
--> SE and bias?
-> what is a bootstrapped confidence interval
--> what can it do
-> how do we create them
-> different types of bootstrapped CI
--> standard t interval, approx classical, swapped SE, percentile, Bias-corrected, BCa
---> for sample mean or corr (check example sheet)

Bootstrapping is a statistical method of resampling that allows the estimation of a test statistic from an unknown distribution. In particular, bootstrapping is a computational heavy method which is useful for many different situations.

First, we will introduce the non-parametric bootstrap. Suppose we have a random sample $X = (x_1,x_2,\dots,x_n)$ from our unknown distribution, $F$ and a statistic of interest $\hat{\theta} = \hat{\theta}(X)$. Ideally, the desired test statistic could be found by repeatedly sampling new reproductions of $X$ from $F$. However $F$ is unknown so this is not possible. The non-parametric bootstrap creates an estimate $\hat{F}$ from $F$ using our sample $X$ without making any parametric assumptions (such as distribution). Therefore, the bootstrap sample could be represented as $X^* = (x^*_1, x^*_2, \dots, x^*_n)$ where each $x^*_i$ is sampled randomly with equal probability and with replacement from $\{x_1,x_2,\dots,x_n\}$. From this bootstrap sample, a bootstrap replication of the test statistic can be computed using $\hat{\theta}^* = \hat{\theta}(X^*)$. A large number, $B$, of bootstrap samples are drawn independently and the corresponding bootstrap replication of the test statistic is calculated. $$\hat{\theta}^{*b} = \hat{\theta}(X^{*b}) \text{ for } b = 1,2, \dots, B$$. The bootstrap estimate of the test statistic is the empirical value of the test statistic from all of the $\hat{\theta}^{*b}$ replications. As $B$ increases, $\hat{F}$ approaches $F$ which means that the tests statistic of interest approaches its true value as well.

SHOULD I ADD ABOUT PARAMETRIC BOOTSTRAP

Confidence intervals are tools that are used to estimate a parameter. Specifically, a confidence interval gives a range in which the true value of the parameter may lie. An $\alpha$-level standard confidence interval is given by $$\hat{\theta} \pm z_{\alpha}\hat{\sigma}$$ where $\hat{\theta}$ is a point estimate of the parameter of interest $\theta$, $\hat{\sigma}$ is the estimate of the standard deviation of $\hat{\theta}$ and $z_{\alpha}$ is the $(100 *\alpha)$th percentile of the normal deviation. We say that the confidence interval constructed in this manner has a chance of capturing the true parameter with a probability of $\alpha$.

The standard confidence interval is built based on the assumption that the distribution from which we are sampling is Normal. This means that for an unknown distribution, the standard confidence interval could present an unmeaningful range. However, the same process can be used with bootstrap sampling to form the bootstrap percentile method.

### 2022-11-17 project/PaperTemplate/paper.tex
Almost done w percentile method

>>>>

\hypertarget{exposition}{%
\section{Exposition}\label{exposition}}

The portion of the paper where you describe the new technique as though
you were teaching it to a classmate (with whatever name you want to give
it - Literature, Background, or Exposition) will be based on your
annotated bibliography. You can add sources to what you already have in
the annotated bibliography (especially if my feedback says you need
to!). To be sure that you are on track with the exposition, a full draft
of this portion of the paper is due before Thanksgiving break. This will
also help with incorporating proper citation early in the writing
process, as you'll have a bibliography that we can implement for this
portion of the paper at a minimum.

Exposition -\textgreater{} what is a bootstrap --\textgreater{}
parametric --\textgreater{} non-parametric --\textgreater{} briefly:
what is jackknife nah --\textgreater{} SE and bias? -\textgreater{} what
is a bootstrapped confidence interval --\textgreater{} what can it do
-\textgreater{} how do we create them -\textgreater{} different types of
bootstrapped CI --\textgreater{} standard t interval, approx classical,
swapped SE, percentile, Bias-corrected, BCa ---\textgreater{} for sample
mean or corr (check example sheet)

Bootstrapping is a statistical method of resampling that allows the
estimation of a test statistic from an unknown distribution. In
particular, bootstrapping is a computational heavy method which is
useful for many different situations.

First, we will introduce the non-parametric bootstrap. Suppose we have a
random sample \(X = (x_1,x_2,\dots,x_n)\) from our unknown distribution,
\(F\) and a statistic of interest \(\hat{\theta} = \hat{\theta}(X)\).
Ideally, the desired test statistic could be found by repeatedly
sampling new reproductions of \(X\) from \(F\). However \(F\) is unknown
so this is not possible. The non-parametric bootstrap creates an
estimate \(\hat{F}\) from \(F\) using our sample \(X\) without making
any parametric assumptions (such as distribution). Therefore, the
bootstrap sample could be represented as
\(X^* = (x^*_1, x^*_2, \dots, x^*_n)\) where each \(x^*_i\) is sampled
randomly with equal probability and with replacement from
\(\{x_1,x_2,\dots,x_n\}\). From this bootstrap sample, a bootstrap
replication of the test statistic can be computed using
\(\hat{\theta}^* = \hat{\theta}(X^*)\). A large number, \(B\), of
bootstrap samples are drawn independently and the corresponding
bootstrap replication of the test statistic is calculated.
\[\hat{\theta}^{*b} = \hat{\theta}(X^{*b}) \text{ for } b = 1,2, \dots, B\].
The bootstrap estimate of the test statistic is the empirical value of
the test statistic from all of the \(\hat{\theta}^{*b}\) replications.
As \(B\) increases, \(\hat{F}\) approaches \(F\) which means that the
tests statistic of interest approaches its true value as well.

SHOULD I ADD ABOUT PARAMETRIC BOOTSTRAP

Confidence intervals are tools that are used to estimate a parameter.
Specifically, a confidence interval gives a range in which the true
value of the parameter may lie. An \(\alpha\)-level standard confidence
interval is given by \[\hat{\theta} \pm z_{\alpha}\hat{\sigma}\] where
\(\hat{\theta}\) is a point estimate of the parameter of interest
\(\theta\), \(\hat{\sigma}\) is the estimate of the standard deviation
of \(\hat{\theta}\) and \(z_{\alpha}\) is the \((100 *\alpha)\)th
percentile of the normal deviation. We say that the confidence interval
constructed in this manner has a chance of capturing the true parameter
with a probability of \(\alpha\).

The standard confidence interval is built based on the assumption that
the distribution from which we are sampling is Normal. This means that
for an unknown distribution, the standard confidence interval could
present an unmeaningful range. However, the same process can be used
with bootstrap sampling to form the bootstrap percentile method.
